\documentclass[10pt,twocolumn]{article}

\usepackage{times}
\usepackage{fullpage}

\usepackage{booktabs}  % for \midrule
%\usepackage{subfigure}
\usepackage{balance}
\usepackage{graphicx}
\usepackage{xspace}
%\usepackage{pslatex}
%\usepackage{pifont}
%\usepackage{multirow}
%\usepackage{array}
%\usepackage{booktabs}
%\usepackage{cite}
\usepackage{url}
%\usepackage{cancel}
\usepackage{color,colortbl}
%\usepackage{microtype}
%\usepackage{textcomp}% http://ctan.org/pkg/textcomp
\usepackage{tabularx}
\usepackage{framed}
\usepackage[]{algorithm2e}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\usepackage{algorithmic}

\usepackage{listings}
%\usepackage{scrextend}
%\usepackage{mathtools}
\usepackage{pbox}
\usepackage{amsmath}

\let\labelindent\relax
\usepackage{enumitem}

\usepackage{tikz}
\usetikzlibrary{arrows,automata}
\usetikzlibrary{calc,positioning}
\usepackage{lipsum,adjustbox}


%\usepackage{tikz}
%\usepackage{decorations.pathmorphing}
%\usepackage{assymb}

\usepackage[labelfont=bf]{caption}

\usepackage{caption}
\usepackage{subcaption}
\usepackage{cleveref}
\captionsetup[subfigure]{subrefformat=simple,labelformat=simple}

%\theoremstyle{plain}
\newtheorem{theorem}{\bf{Theorem}}%[section]
\newtheorem{lemma}[theorem]{\bf{Lemma}}
\newtheorem{corollary}[theorem]{\bf{Corollary}}
\newtheorem{proofl}[theorem]{\bf{Proof}}
\newtheorem{proposition}[theorem]{\bf{Proposition}}

%\theoremstyle{definition}
\newtheorem{definition}{\bf{Definition}}%[section]
\newtheorem{observation}{\bf{Observation}}%[section] 

%\theoremstyle{remark}
\newtheorem{example}{\bf{Example}}
\newtheorem{notation}{\bf{Notation}}
\newtheorem{fact}{\bf{Fact}}

\usepackage{listings}
%%\usepackage{listings-golang}
\usepackage{color}

%\usepackage{sectsty}
%\sectionfont{\fontsize{12}{15}\selectfont}


\newcommand\mypara[1]{\vspace{.3em}\noindent\textbf{#1}}
\newcommand{\urlwofont}[1]{\urlstyle{same}\url{#1}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Useful reviewing/feedback annotations
\input{annotations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\title{Cuckoo for Clients: Disaggregated Cuckoo Hashing}
%\author{WORDS '21 Submission \#3}
% \author{Stewart Grant and Alex C. Snoeren\\ UC San Diego}
\author{ATC '24 Submission \#820}
\date{}

\maketitle

\section*{Abstract}

Memory disaggregation promises high resource utilization,
and efficient resource sharing. However designing fully
disaggregated systems remains challenging due to complex
serialization, high latency, and failures. Key-value store 
indexes often adopt a partially disaggregated approach
where writes to the index are routed through a CPU for
serialization, while reads are made directly to memory.
Fully disaggregation assumes no such CPU and must serialize
writes entirely with clients.

In this paper we describe the first fully disaggregated
lock based cuckoo hash. Prior work avoids locks in favor of
optimistic concurrency as locks can have large critical
sections and complex failures. We show that that with
careful design locks can have higher performance than
opportunistic algorithms and recover from failures quickly.
We develop a locality based hashing algorithm which enables
fast reads, and efficient locking. We compare our
performance against state of the art key value stores and
show gains on an YCSB benchmarks against all systems
achieving between 1.4x to 10x on write heavy workloads and
1.3x to 2.2x on read heavy workloads.


% with careful data structure and protocol design, as well as
% the architecture of modern RDMA NICs traditional locking
% strategies can perform better than state of the art
% optimistic concurrency algorithms. We demonstrate this
% through the design of a remote memory key value store based
% on cuckoo hashing. Our cuckoo hashing algorithm (rcuckoo)uses dependent,
% rather than independent hash functions to increase the
% probability that both hashes of a key will be
% close in the hash table. This locality enables fast lock
% acquisition and release. We demonstrate that rcuckoo
% outperforms optimistic concurrency algorithms by 2x in
% terms of throughput and up to a 2x improvement on read
% latency.

\input{intro}
\input{background}
\input{body}
\input{problems}
\input{design}
\input{evaluation}
\input{limitation}
\input{conclusion}

% \section*{Acknowledgments}

% Thanks for everyone that supported me. Thanks to Pengfei Zuo
% for assistance in replicating results from the original RACE
% paper.


\balance
\vspace{-0.3cm}
{\footnotesize \bibliographystyle{acm}
\bibliography{paper}}
\vspace{-0.5cm}

\end{document}
