\documentclass[10pt,twocolumn]{article}

\usepackage{times}
\usepackage{fullpage}

\usepackage{booktabs}  % for \midrule
%\usepackage{subfigure}
\usepackage{balance}
\usepackage{graphicx}
\usepackage{xspace}
%\usepackage{pslatex}
%\usepackage{pifont}
%\usepackage{multirow}
%\usepackage{array}
%\usepackage{booktabs}
%\usepackage{cite}
\usepackage{url}
%\usepackage{cancel}
\usepackage{color,colortbl}
%\usepackage{microtype}
%\usepackage{textcomp}% http://ctan.org/pkg/textcomp
\usepackage{tabularx}
\usepackage{framed}
\usepackage[]{algorithm2e}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\usepackage{algorithmic}

\usepackage{listings}
%\usepackage{scrextend}
%\usepackage{mathtools}
\usepackage{pbox}
\usepackage{amsmath}

\let\labelindent\relax
\usepackage{enumitem}

\usepackage{tikz}
\usetikzlibrary{arrows,automata}
\usetikzlibrary{calc,positioning}
\usepackage{lipsum,adjustbox}


%\usepackage{tikz}
%\usepackage{decorations.pathmorphing}
%\usepackage{assymb}

\usepackage[labelfont=bf]{caption}

\usepackage{caption}
\usepackage{subcaption}
\usepackage{cleveref}
\captionsetup[subfigure]{subrefformat=simple,labelformat=simple}

%\theoremstyle{plain}
\newtheorem{theorem}{\bf{Theorem}}%[section]
\newtheorem{lemma}[theorem]{\bf{Lemma}}
\newtheorem{corollary}[theorem]{\bf{Corollary}}
\newtheorem{proofl}[theorem]{\bf{Proof}}
\newtheorem{proposition}[theorem]{\bf{Proposition}}

%\theoremstyle{definition}
\newtheorem{definition}{\bf{Definition}}%[section]
\newtheorem{observation}{\bf{Observation}}%[section] 

%\theoremstyle{remark}
\newtheorem{example}{\bf{Example}}
\newtheorem{notation}{\bf{Notation}}
\newtheorem{fact}{\bf{Fact}}

\usepackage{listings}
%%\usepackage{listings-golang}
\usepackage{color}

%\usepackage{sectsty}
%\sectionfont{\fontsize{12}{15}\selectfont}


\newcommand\mypara[1]{\vspace{.3em}\noindent\textbf{#1}}
\newcommand{\urlwofont}[1]{\urlstyle{same}\url{#1}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Useful reviewing/feedback annotations
\input{annotations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\title{Remote Memory Cuckoo Hashing}
%\author{WORDS '21 Submission \#3}
\author{Stewart Grant and Alex C. Snoeren\\ UC San Diego}
\date{}

\maketitle

\section*{Abstract}

Far memory data structures eschew locks in favor of
optimistic concurrency as locks increase critical section
size and messages. Optimistic concurrency unfortunately
comes at the cost of high failure rates, complex protocols,
and the need to perform data updates at small fixed sizes
(64 bits for compare and swap). In this work we show that
with careful data structure and protocol design, as well as
the architecture of modern RDMA NICs traditional locking
strategies can perform better than state of the art
optimistic concurrency algorithm. We demonstrate this
through the design of a remote memory key value store based
on cuckoo hashing. Our cuckoo hashing algorithm (rcuckoo)
uses dependent, rather than independent hash functions to
increase the probability that a keys two buckets are close
in the hash table. This locality enables fast lock
acquisition and release. We demonstrate that rcuckoo
outperforms optimistic concurrency algorithms by 2x in
terms of throughput and up to a 2x improvement on read
latency, as well as achieving higher fill factors.

\input{intro}
\input{background}
\input{body}
\input{problems}
\input{design}
\input{implementation}
\input{evaluation}
\input{conclusion}

\section*{Acknowledgments}

Thanks for everyone that supported me. Thanks to Pengfei Zuo
for assistance in replicating results from the original RACE
paper.


\balance
\vspace{-0.3cm}
{\footnotesize \bibliographystyle{acm}
\bibliography{paper}}
\vspace{-0.5cm}

\end{document}
