\section{Limitations}
\label{sec:limations}

\subsection{replication and persistance}
At the time of writing Rcuckoo does not support multiple
memory nodes for replication and is not designed for
persistance. No aspect of RCuckoo's algorithm prevents the
use of multiple replicas. As Rcuckoo uses lock based
protection, replicated updates can be broadcast by writes to
each replica prior to releasing locks. Rcuckoo's index is
not designed for persistance. As Rcuckoo is primarily an
index, we see it as compatable with the persistance
strategies of other disaggregated projects. For instance
RCuckoo could easily make use of Clover's persistent extent
algorithm with no changes to RCuckoo's index structure.

\subsection{Replication, and scalability} 
\todo{no real replication probabily delete, consider moving
to future work / limiations} At the time of writing RCuckoo
does not support replication although replication is in no
way a complication for our existing algorithms. On inserts
clients aquire locks from a master memory node as described
in section~\ref{sec:insert}, after locks are acquired on the
master node updates, deletes, or cuckoo paths are broadcast
to replicas. Replication requires a clients to wait for
responses from replicas before issuing unlock messages as
the client can not rely on RDMA RC connection in order
delivery across the multiple replica connections.

\todo{We don't span multiple memory nodes} When using
multiple memory machines each machine is initialized with an
equal portion of the cuckoo index and lock table. Clients
calculate which machine to issue their requests to when
generating requests.


\subsection{Client Scalability} RCuckoo's algorithm relies
on the semantics of in order delivery for the correctness of
it's locking and reading algorithms. RDMA NIC's have hard
caps on the number of reliable connections they support
~\todo{(~65k)} these limitations are fundamental to the
cache size on the RDMA NIC~\cite{erpc,faast}, although cache
sizes have steadily increased~\cite{storm}. RDMA unreliable
connections currently do not support one-sided verbs making
them unusable for disaggregated applications.
