\documentclass[10pt,twocolumn]{article}

\usepackage{times}
\usepackage{fullpage}

\usepackage{booktabs}  % for \midrule
%\usepackage{subfigure}
\usepackage{balance}
\usepackage{graphicx}
\usepackage{xspace}
%\usepackage{pslatex}
%\usepackage{pifont}
%\usepackage{multirow}
%\usepackage{array}
%\usepackage{booktabs}
%\usepackage{cite}
\usepackage{url}
%\usepackage{cancel}
\usepackage{color,colortbl}
%\usepackage{microtype}
%\usepackage{textcomp}% http://ctan.org/pkg/textcomp
\usepackage{tabularx}
\usepackage{framed}
\usepackage[]{algorithm2e}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\usepackage{algorithmic}

\usepackage{listings}
%\usepackage{scrextend}
%\usepackage{mathtools}
\usepackage{pbox}
\usepackage{amsmath}

\let\labelindent\relax
\usepackage{enumitem}

\usepackage{tikz}
\usetikzlibrary{arrows,automata}
\usetikzlibrary{calc,positioning}
\usepackage{lipsum,adjustbox}


%\usepackage{tikz}
%\usepackage{decorations.pathmorphing}
%\usepackage{assymb}

\usepackage[labelfont=bf]{caption}

\usepackage{caption}
\usepackage{subcaption}
\usepackage{cleveref}
\captionsetup[subfigure]{subrefformat=simple,labelformat=simple}

%\theoremstyle{plain}
\newtheorem{theorem}{\bf{Theorem}}%[section]
\newtheorem{lemma}[theorem]{\bf{Lemma}}
\newtheorem{corollary}[theorem]{\bf{Corollary}}
\newtheorem{proofl}[theorem]{\bf{Proof}}
\newtheorem{proposition}[theorem]{\bf{Proposition}}

%\theoremstyle{definition}
\newtheorem{definition}{\bf{Definition}}%[section]
\newtheorem{observation}{\bf{Observation}}%[section] 

%\theoremstyle{remark}
\newtheorem{example}{\bf{Example}}
\newtheorem{notation}{\bf{Notation}}
\newtheorem{fact}{\bf{Fact}}

\usepackage{listings}
%%\usepackage{listings-golang}
\usepackage{color}

%\usepackage{sectsty}
%\sectionfont{\fontsize{12}{15}\selectfont}


\newcommand\mypara[1]{\vspace{.3em}\noindent\textbf{#1}}
\newcommand{\urlwofont}[1]{\urlstyle{same}\url{#1}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Useful reviewing/feedback annotations
\input{annotations}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\title{Remote Memory Cuckoo Hashing}
%\author{WORDS '21 Submission \#3}
\author{Stewart Grant and Alex C. Snoeren\\ UC San Diego}
\date{}

\maketitle

\section*{Abstract}

Memory disaggregation promises high resource utilization,
and efficient resource sharing. However designing fully
disaggregated systems remains challenging due to complex
serialization and high latency. Key-value store indexes
often adopt a ~\textit{partially disaggregated} approach
where updates to the index are routed through a CPU for
serialization, while reads are made directly to memory.
Fully disaggregated indexes assume no such CPU and must
serialize updates entirely with remote clients.

This paper focuses on the design of a fully disaggregated
lock-based key-value index based on cuckoo hashing. Prior
work avoids locks in favor of optimistic concurrency as
locks can have large critical sections and quickly
bottleneck performance. We show that that with careful
design locking schemes can enable higher performance than
opportunistic schemes even under contention.

To achieve efficient locking we develop a new cuckoo hashing
scheme that increases locality of keys in the table. Using
this locality we design a dense and efficient lock table which 
uses NIC device memory. Locality also improves how search can
find short insertion paths into the cuckoo table. We 
demonstrate the performance benefit of our design by comparing 
to both fully disaggregated and partially disaggregated key value 
stores. We show performance gains on an YCSB benchmarks 
against all systems achieving between 1.4x to 10x on write heavy 
workloads and 1.3x to 2.2x on read heavy workloads.


% with careful data structure and protocol design, as well as
% the architecture of modern RDMA NICs traditional locking
% strategies can perform better than state of the art
% optimistic concurrency algorithms. We demonstrate this
% through the design of a remote memory key value store based
% on cuckoo hashing. Our cuckoo hashing algorithm (rcuckoo)uses dependent,
% rather than independent hash functions to increase the
% probability that both hashes of a key will be
% close in the hash table. This locality enables fast lock
% acquisition and release. We demonstrate that rcuckoo
% outperforms optimistic concurrency algorithms by 2x in
% terms of throughput and up to a 2x improvement on read
% latency.

\input{intro}
\input{background}
\input{body}
\input{problems}
\input{design}
\input{implementation}
\input{evaluation}
\input{limitation}
\input{conclusion}

\section*{Acknowledgments}

Thanks for everyone that supported me. Thanks to Pengfei Zuo
for assistance in replicating results from the original RACE
paper.


\balance
\vspace{-0.3cm}
{\footnotesize \bibliographystyle{acm}
\bibliography{paper}}
\vspace{-0.5cm}

\end{document}
